\documentclass[11pt]{article}

\usepackage{fancyhdr}
\usepackage[margin=.9in]{geometry}
\usepackage{amsmath}
\usepackage{enumitem}

\linespread{1.3}
\setlength{\parindent}{0pt}

% ===========================================================================
% Header / Footer
% ===========================================================================
\pagestyle{fancy}
\lhead{\scriptsize  CSC 212: Data Structures and Abstractions - Fall 2017}\chead{}\rhead{\scriptsize Weekly Problem Set \#1}
\lfoot{}\cfoot{\scriptsize \thepage~of~\pageref{r:lastpage}}\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% ===========================================================================
% ===========================================================================
\begin{document}
\thispagestyle{empty}

% ===========================================================================
\begin{center}
    {\Large\bf CSC 212: Data Structures and Abstractions}\\
    \medskip
    {\Large\bf University of Rhode Island}\\
    \bigskip
    {\Large\bf Weekly Problem Set \#1}
\end{center}

\vspace{25pt}

This assignment is due Wednesday 1/31 before lab. Please turn in neat, and organized, answers hand-written on standard-sized paper without any fringe.  Problem set 1 is all about strings and arrays, these are fundamental data types. They are incredibly important to understand if you wish to be sucessful in this class! 

\begin{enumerate}[leftmargin=*]

% 1
\item Write a function that returns the length of a given string. For example, given \verb|"Test"|, return \verb|4|.

% GeeksForGeeks
\item Using the function you defined above, create another function that returns true if a given string is a palindrome, and false if it is not. For example, \verb|"ABCBA"| is a palindrome, \verb|"ABC"| is not.

% GeeksForGeeks
\item Define a function that returns the most frequently occuring character inside of a string. What would you have to change in order for this program to return the least frequently occuring character? 

% GeeksForGeeks
\item Write a function that returns the number of words in a given string.

% CodeForWin
%\item Define a function to \textit{toggle} the case of a given string. (Running this twice on a given string should yield the starting string)

% CodeForWin
\item Write a function that returns a missing number in an array of integers ranging from 1 to $n$. For example, given $[1, 2, 3, 5]$, ouput \verb|4|. 

% CodeForWin
\item Define a function that returns the average of the minimum and maximum elements in an unsorted array of integers. How would this code change if the array were sorted?

\end{enumerate}

The following exercises are considered {\it optional}.  You don't need to report answers on these.

% CodeForWin
\item Write a program that removes any duplicate integers from an array. For example, given $[1, 2, 2, 3, 4, 2, 5]$, the program should print $[1, 2, 3, 4, 5]$.

% CodeForWin
\item How would you implement a function that reverses a given array in place? Write a high-level psuedo-code for this function.

%
\item Briefly describe the difference between an array of integers and characters. How would you find their length? Space Requirements?

%
%\item Using psuedo code, write a function that converts a string of numbers to their decimal equivalent. EX: Given \verb|"1 2 3 4 5"|, generate the array \verb|[1, 2, 3, 4, 5]|.

\end{enumerate}

\label{r:lastpage}

\end{document}
    
