\documentclass[11pt]{article}

\usepackage{listings}
\usepackage{fancyhdr}
\usepackage[margin=.8in]{geometry}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{hyperref}

\linespread{1}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{20pt}

% ===========================================================================
% Header / Footer
% ===========================================================================

\pagestyle{fancy}
\lhead{\scriptsize  CSC 212: Data Structures and Abstractions - Spring 2018}\chead{}\rhead{\scriptsize Weekly Problem Set \#12}
\lfoot{}\cfoot{\scriptsize \thepage~of~\pageref{r:lastpage}}\rfoot{}
\renewcommand{\headrulewidth}{0.25pt}
\renewcommand{\footrulewidth}{0.25pt}

% ===========================================================================
% ===========================================================================
\begin{document}
\thispagestyle{empty}

% ===========================================================================
\begin{center}
    {\Large\bf CSC 212: Data Structures and Abstractions}\\
    \medskip
    {\Large\bf Spring 2018}\\
    \medskip
    {\Large\bf University of Rhode Island}\\
    \bigskip
    {\Large\bf Weekly Problem Set \#12}
\end{center}

Due Thursday 4/26 before class. Please turn in neat, and organized, answers hand-written on standard-sized paper \textbf{without any fringe}. At the top of each sheet you hand in, please write your name, and ID.
The only library you're allowed to use in your answers is \verb|iostream|.

\section{2-3 Trees}
\begin{enumerate}
    \item Draw a 2-3 tree after inserting the following elements: [10, 5, 12, 8, 19, 6, 2, 11, 15, 9, 7]

    \item Write a search algorithm for a 2-3 tree.

    \item True or False, while inserting nodes into a 2-3 tree, all required transformations are purely local. Explain your response.
\end{enumerate}

\section{Red-Black Trees}
\begin{enumerate}
    \item Draw a Red-Black tree after inserting the following elements: [1, 2, 3, 4, 5]
    
    \item Draw another Red-Black tree after inserting the following elements: [23, 9, 5, 22, 7, 12, 28, 17, 20, 16]

    \item Can Red-Black Trees be represented as 2-3 trees? If so, how?

    \item Why is it advantageous to have balanced trees?

    \item True or false, as you insert nodes into a Red-Black Tree, the height is strictly increasing?
\end{enumerate}

\label{r:lastpage}

\end{document}
    
